Final Project Draft #2

### 2022-04-26 draft2.Rmd
Cat Alt Text

```{r}
healthy_data_dot <- healthy_data_2 [-c(23),]

>>>>

```{r, fig.alt= "This graph displays various cities with their own color coded dot based on happiness level (x axis) and weekly hours worked (y axis). There is a loose correlation between greater happiness and fewer weeky work hours. The dots are able to be scrolled over with the cursor, displaying exact happiness level, exact work hours, and city."}
healthy_data_dot <- healthy_data_2 [-c(23),]
